The \project{unRAVE} catalog

### 2016-09-08 article/unrave.tex
Add repeat visits figure

@@

\stub{In Figure \ref{fig:test-set-repeats} we look at the difference as a function of SNR}

@@

\begin{figure*}[p]
\caption{The RMS of the test set labels as a function of S/N ratio for repeated stars in the test set.\label{fig:test-set-repeats}}
\end{figure*}

>>>>

% Gilmore, Matijevic, McMillan, Siviero, Wojno

@@

\stub{In Figure \ref{fig:repeat-visits} we look at the difference as a function of SNR}

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/repeat-visits.pdf}
\caption{The RMS of the test set labels as a function of S/N ratio for repeated stars in the test set.\label{fig:repeat-visits}}
\end{figure*}
